Indicators for Ecosystem Condition in Norway

### 2023-04-14 index.Rmd
build_book_test_license

---
title: "Indicators for Ecosystem Condition in Norway"
author: "Anders L. Kolstad"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: https://ninanor.github.io/ecosystemCondition/index.html
# cover-image: path to the social sharing image like images/cover.jpg
description: |
  This is a site for documenting the analyses related to the development and design of ecosystem condition indicators.
biblio-style: apalike
csl: chicago-fullnote-bibliography.csl
---

@@

On this site you may view the nitty gritty details for how certain indicators for ecosystem condition for Norway has been calculated.

@@

>>>>

---
title: "Indicators for Ecosystem Condition in Norway"
author: "Anders L. Kolstad"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: https://ninanor.github.io/ecosystemCondition/index.html
cover-image: images/Picture1.png
description: |
  This is a site for documenting the analyses related to the development and design of ecosystem condition indicators.
biblio-style: apalike
csl: chicago-fullnote-bibliography.csl
---

@@

On this site you may view the details for how certain indicators for ecosystem condition for Norway have been calculated.

@@

## Citation {.unnumbered}

To cite this book please use the following citation:

Kolstad, A.L., Topper, J. Grainger, M.J., Sandvik, H. Indicators for Ecosystem Condition in Norway. https://ninanor.github.io/ecosystemCondition/index.html.doi [TBA]

## License

The book is licensed under a [CC By 4.0 licence](https://creativecommons.org/licenses/by/4.0/) which means that you can share and adapt the material
for any purpose. However, you must give appropriate credit, provide a link to the license, and indicate if changes were made. You can not add additional restrictions on the material even when adapted.
